---
title: "lab 8 key"
author: "Allison Horst"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data

```{r}
homes <- read_csv(here("slo_homes.csv"))
```

A little bit of cleaning: 

Make a subset called homes_sub that only contains observations (rows) where the city is: 

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status. 

```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code: eval = FALSE

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.2) +
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City, and the point shape by sale status. 

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

# How would I explore diagnostic plots? 
plot(homes_lm1)
```

Try another model (homes_lm2) where we simplify this a bit: 

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

# Or just call this in the Console
homes_lm2

plot(homes_lm2)
```

Find the AIC value of each model: 

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think might make sense, check out & compare the model fit, outputs and AIC value. 

```{r}
homes_lm3 <- lm(Price ~ SqFt + City + Status + Bedrooms, data = homes_sub)

summary(homes_lm3)
AIC(homes_lm3)
```

Use `modelsummary` to show model outputs side-by-side: 

If you use modelsummary to return model outputs of multiple models, it wants you to feed it to it as a list. 
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```




